Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/discussion.tex
working on discussion

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{posneg}
\caption{The amount of comments by score classified by the binary classifier.}
\label{fig:binary}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{posneg}
\caption{The amount of comments by score classified by the binary classifier.}
\label{fig:binary}
\end{figure}
\subsection*{Can other text mining techniques be used to classify discussions?}
To find relevance between comments and the corresponding commit message, topic modeling technique can be used as the study of \cite{Barua2012a}. This technique discovers topics for a given collection of documents. However, in MCR context, the documents generally is short descriptions and short discussions. 
The topic modeling technique would generate topics that include diverse actual topics of documents since the content of documents is insufficient to determine. We have applied Latent Dirichlet allocation (LDA), which is a well-known model of topic modeling techniques, on our data set. We found that the generated topics were diverse and some of them cannot did not have a relation between documents and their topics. Therefore, the topic modeling cannot be used to classify discussions. Others techniques will be investigated in our future work to improve our approach.

\subsection{Threat to Validity}

### 2014-07-28 sections/results.tex
working on discussion

Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores. The classification of useless comments also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments. Due to subjective and error-prone manual classification, these comments were not received three voting scores. This suggests us to re-examine the comments again. \pick{I'm not sure if comments with vote 2 are highly classified as useful and comments with vote 1 are highly classified as useless, what will we do.}

>>>>

Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores. The classification of useless comments also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments. Since the manual classification can be, these comments were not received three voting scores.
